\documentclass[PROP_AGutteridge_CS.tex]{subfiles}
\begin{document}

\chapter{Conclusion}
\section{Development Plan}
For each of the four key objectives a set of deliverables were determined; this granularisation of the project into smaller, more manageable segments enables a more detailed work plan to be set out. As these can be read in the previous section, the total timings of each objective are summarised as follows:

\begin{table}[h]
\noindent
\centering
\begin{tabular}{ | l | p{2.5cm} | p{2.5cm} | }
	\hline
	\bf{Description} 				& \bf{Shortest est. timeframe} & \bf{Longest est. timeframe}\\ \hline
	Semantic analysis tools 			& 1.5 weeks 		& 3 weeks\\ 
	Geocoding of addresses 			& 1 week 			& 2 weeks\\ 
	Implementation of a web framework 	& 1.5 weeks 		& 3 weeks\\ 
	Data Visualisation 				& 3.5 weeks 		& 6 weeks\\ \hline
	\bf{Finished project} 				& \bf{7.5 weeks} 	& \bf{14 weeks}\\ \hline
	Project report 					& 2 weeks 		& 3 weeks\\ \hline
\end{tabular}
\noindent
\end{table}

I plan to start work on the project on Monday 8th June, 2015, which allows for 14 weeks of development and writing time in total. The report will be written throughout this time, but I have allowed for 2--3 weeks dedicated time before the hand-in date. 

\section{Additional Features}
As this project will be my first experience with web development, I do not expect to have a considerable amount of excess time after completion of the objectives. However, there are a number of ways in which the web application could be extended in order to further the user's search experience. In brief, these are:
\begin{itemize}
\item{Development of additional front-end interactive elements for filtering and selecting citations}
\item{Ranking of relevant papers according to number of citations. As discussed in 'Comparison of Bibliographic Resources', Google Scholar is a potential source of data.}
\item{Creation of user accounts, allowing users to login and save searches, citations or keywords.}
\item{Name-entity disambiguation of authors. This was initially included in the project aims but was subsequently found to be an active area of research\cite{shin}, and is therefore most likely beyond the capability of an MSc student project.}
\end{itemize}

\end{document}